SoK: Transparent Dishonesty: front-running attacks on Blockchain.

### 2019-02-08 frontrunning/Latex/sections/paper.tex
[frontrunning] modifications on cryptokitties specific front-running

% SHAYAN: TODO: Continue here! 
Specific to Cryptokitties protocol, they can breed and give birth. Anyone calling \textit{giveBirth()} quickly after the expected birthing time, will receive the birthing reward and give birth to the new cryptokitten which will be owned by the mother's owner.

@@

~\cite{zhou2018erays}

% Shayan TODO:
% remove most of the text above and replace it with references: https://hackernoon.com/how-we-made-100k-trading-cryptokitties-2d69aebe715b
% disuss the application specific front-running, which is with giveBirth() function and front-running other calls
% https://medium.com/block-science/exploring-cryptokitties-part-2-the-cryptomidwives-a0df37eb35a6
% maybe: https://blog.kleros.io/generalized-ethereum-frontrunners-an-implementation-and-a-cheat/

>>>>

%Shayan -> Jeremy: does this make sense? there are more details in the references that due to space limitations cannot be discussed here.
Specific to Cryptokitties protocol, they can breed and give birth. When cryptokitties breed, a variable is set on the pregnant cat to indicate what block the pregnancy will be complete. Anyone calling \texttt{giveBirth()} quickly after the expected birthing time, will receive the birthing reward\footnote{As there are no automated function calls in Ethereum, this incentive model --known as \textit{Action Callback}~\cite{klerosGeneralizedFrontrunner2019}-- is used to encourage users to call these functions.}. Even though front-running these calls would not affect the protocol workflow, but it could result in financial profit for front-runners~\cite{zhou2018erays,cryptoMidwivesBot2018}.

@@
